Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-06 paper/main.tex
added lag-CRP description

>>>>

The lag-conditional probability (lag-CRP) curve~\citep{Kaha96} reflects the
probability of recalling a given item after the just-recalled item, as a
function of their relative encoding positions (lag). In other words, a lag of 1
indicates that a recalled item was presented immediately after the previously
recalled item, and a lag of $−3$ indicates that a recalled item came 3 items
before the previously recalled item. For each recall transition (following the
first recall), we computed the lag between the just-recalled word's
presentation position and the next-recalled word's presentation position. We
computed the proportions of transitions (between successively recalled words)
for each lag, normalizing for the total numbers of possible transitions. In
carrying out this analysis, we excluded all incorrect recalls and successive
repetitions (e.g., recalling the same word twice in a row).  This yielded, for each list,
a 1 by number-of-lags ($-15$ to $+15$; 30 lags in total, excluding lags of 0) array of conditional probabilities.
We averaged these probabilities across lists to obtain a single lag-CRP for each participant.
